---
title: "Project3"
author: "sudhan_maharjan, vinayak_patel, Olga_Shiligin"
date: "October 19, 2018"
output: html_document
---

# To Find Most Valued Data Science Skills

## Greetings,

My Name is Vinayak Patel. My team is Olga Shiligin (London) and Sudhan Maharjan (New York). We are
graduate students at CUNY School of Professional Studies.
I am writing to you to request your participation in a brief survey. The Purpose of the survey is find out
most valued data science skills for New data scientist like us.
The survey will be live from Oct 17th to Oct 20th. We are trying to reach many IT Professionals As we
can. Please feel free to forward link in your network. We will really appreciate.
Your participation in the survey is completely voluntary. No personally identifiable information will be
associated with your responses to any reports of these data.
Should you have any comments or questions, please feel free to contact me at

#Get the data from github

```{r}
#getting the csv data from github
datascience_skills <- read.csv("https://raw.githubusercontent.com/Vinayak234/SPS_DATA_607/master/SPS_DATA_607/Project_3/To%20find%20Most%20Valued%20Data%20Science%20Skills.csv", header=TRUE, sep=",")

head(datascience_skills)
```



```{r}
#VIEW THE DATA AND CREATE NAMES
str(datascience_skills)
```

```{r}
#to check how many candidates participated in this survey
library(dplyr)
count(datascience_skills, vars = "Gender")

```

```{r}
#to see how many of the participants were male or female
library(ggplot2)
qplot(Gender, data = datascience_skills, fill = Gender, ylab="Participants")

```

```{r}
#participants willingness to learn data science skills
col9 = 9;
x = datascience_skills[,c(col9)];

names(x) <- c("Willingness to learn data science skills")


#see how many participants wants to learn 
qplot(x, data = datascience_skills, fill = x, ylab="Participants")
```
 

